---
title: "Project 21"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Natalie McGuckin

This project is supposed to be an easy modification of the project example, 
since it is almost time for Spring Break! 

Note:  Do not worry if some of the results have extra spaces.  We can 
deal with that later! 

**1.** Modify the NPS example to extract the city location for every 
National Park.
```{r}
library(RCurl)
library(XML)
myparks <- xpathSApply(htmlParse(getURL("https://www.nps.gov/findapark/index.htm")), "//*/div/select/optgroup/option", xmlGetAttr, "value")
mygoodparks <- myparks[(myparks != "cbpo")&(myparks != "foca")]
mycityextractor <- function(x) {xpathSApply(htmlParse(getURL( paste0("https://www.nps.gov/", x, "/index.htm"))),
                                            "//*/span[@itemprop='addressLocality']", xmlValue)}
myresults <- sapply( mygoodparks, mycityextractor )
head(myresults)

```
Explain solution: Used my city extractor to find cities. 

**2.** Same question, for the state location for every National Park. 
```{r}
mystateextractor <- function(x) {xpathSApply(htmlParse(getURL( paste0("https://www.nps.gov/", x, "/index.htm"))),
                                            "//*/span[@itemprop='addressRegion']", xmlValue)}
myresults <- sapply( mygoodparks, mycityextractor )
head(myresults)
```
Explain solution: Used the resources on piazza and from previous homework to solve solution. Used mystate extractor because we needed a state. 

**3.** Same question, for the zip code for every National Park. 
```{r}
myzipcodeextractor <- function(x) {xpathSApply(htmlParse(getURL( paste0("https://www.nps.gov/", x, "/index.htm"))),
                                            "//*/span[@itemprop='postalCode']", xmlValue)}
myresults <- sapply( mygoodparks, myzipcodeextractor )
head(myresults)
```
Explain solution: Used zipcode extractor to get zip code



