---
title: "class example"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1a. Compute the average distance for the flights on each airline in 2005. 
```{r}
myDF <- read.csv("/depot/statclass/data/dataexpo2009/2005.csv")
pizza <- tapply(myDF$Distance, myDF$UniqueCarrier, mean, na.rm=T)
print(pizza)
```

1b. Sort the result from 1a, and make a dotchart to display the results in sorted order. (Please display all of the values in the dotchart.)
```{r}
dotchart(sort(pizza))
```



2a. Compute the average total amount of the cost of taxi rides in June 2017, for each pickup location ID. 

```{r}
taxi <- read.csv("/depot/statclass/data/taxi2018/yellow_tripdata_2017-06.csv")
pizza2 <- tapply(taxi$total_amount,taxi$PULocationID,mean,na.rm=TRUE)
print(pizza2)
```


2b. Sort the result from 2a, and make a dotchart to display the results in sorted order. (Please ONLY display the results with value bigger than 80.)
```{r}

dotchart(sort(pizza2[pizza2>80]))
```


