---
title: "Project.7"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#1. 
Use the Batting.csv file (inside the "core" folder)
    to discover who is a member of the 40-40 club,
    namely, who has hit 40 home runs and also has
    (simultaneously) stolen 40 bases in the same season.
    
```{r}
myDF <- read.csv ("Downloads/baseballdatabank-master/core/Batting.csv")
myDF[myDF$HR>=40 & myDF$SB>=40,]
```

#2. 
Make a plot that depicts the total number of home runs per year
    (across all players on all teams).  The plot should have the years
    as the labels for the x-axis, and should have the number of home runs
    as the labels for the y-axis.
```{r}
v <- tapply(myDF$HR,myDF$yearID,sum)
plot(names(v),v,xlab = "years",ylab = "HR")
```

#3
```{r}
#a.
myBatting <- read.csv ("Downloads/baseballdatabank-master/core/Batting.csv")
myPeople <- read.csv ("Downloads/baseballdatabank-master/core/People.csv")
myDF <- merge(myBatting, myPeople, by="playerID")
#b.
Fullname <- paste(myDF$nameFirst,myDF$nameLast)
myDF$fullname <- Fullname
#c
myDF[myDF$HR>=40 & myDF$SB>=40,]